Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-09-02 doc/GMP2015/revision_3/s01_introduction.tex
The submitted revision 3.

We additionally conjecture that versions of \frontier, a previously given, bottom-up, polynomial time method for obtaining DR-plans with various desired properties~\cite{hoffman2001decompositionI, hoffman2001decompositionII,lomonosov2004graph,sitharam2005combinatorial}, in fact generate an optimal DR-plan for non-overconstrained systems.

@@

The last Section~\ref{sec:conclusion} concludes the paper, and Section \ref{sec:open} lists open problems and conjectures. In particular, we conjecture that the methods of Section~\ref{sec:DRP} extend in fact to a large class of (hyper)graphs, formally those with an underlying abstract rigidity matroid in which independence corresponds to some type of sparsity, and maximal independence (rigidity) is a tightness condition.

>>>>

@@

The last Section~\ref{sec:probs_and_conclusion} concludes the paper, and Section \ref{sec:open} lists open problems and conjectures. In particular, we conjecture that the methods of Section~\ref{sec:DRP} extend in fact to a large class of (hyper)graphs, formally those with an underlying abstract rigidity matroid in which independence corresponds to some type of sparsity, and maximal independence (rigidity) is a tightness condition.

### 2015-09-02 doc/GMP2015/revision_3/s03_drp.tex
The submitted revision 3.

In this section and in Section~\ref{sec:recomb}, any reference to a graph $G$ without further specification is assumed to be isostatic (i.e.\ well-constrained or $(k,l)$-tight). Furthermore, we only consider unions and intersections of graphs that are induced subgraphs of a single parent graph $G$. In this case unions and intersections are well defined. For example, the union (resp.\ intersection) of $F_1 = (V_1, E_1)$ and $F_2 = (V_2, E_2)$ is the subgraph of $G$ induced by $V_1\cup V_2$ (resp.\ $V_1\cap V_2$).

@@

    The proof of optimality of a canonical DR-plan is by induction on its height. The base case trivially holds for canonical DR-plans of height 0, i.e.\ for single edges. The induction hypothesis is that canonical DR-plans of height $t$ are optimal for the root node.
    For the induction step consider a canonical DR-plan $\candrpx{C}$ rooted at node $C$ with height $t+1$.
    Notice that $\candrpx{C}$ contains a canonical DR-plan $\candrpx{C_i}$ for the graphs $C_i$ corresponding to each of $C$'s descendent nodes.
    Thus, from the induction hypothesis, we know that the $\candrpx{C_i}$ is optimal for $C_i$.

@@

        \newcommand{\induceonc}[1]{Idc\left(C,#1\right)}
        \renewcommand{\induceonc}[1]{#1}
        \newcommand{\iunion}[1]{\induceonc{I\cup\bigcup_{k\in [N]\setminus\{#1\}}{R_k}}}

@@

\begin{observation}
[Sequential is optimal]
    Any \pseudosequential\ DR-plan of an independent graph is optimal.
\end{observation}

@@

\begin{definition}
[\Branch]
    Given a \pseudosequential\ DR-plan $P_G$ for an isostatic graph $G$, and an edge $e \in G$, the \branchGePG\ is the subtree of the DR-plan consisting of the path from the leaf containing $e$ to the root containing $G$, together with the children of all the nodes on this path, which are the leaves of \branchGePG. See Figure~\ref{fig:seq_proof} for examples.
\end{definition}

@@

    Case (1):
    $D$ and $L$ are edge disjoint, and $D$ contains
    (1a) no elements,
    (1b) exactly one element, or
    % originally 1a and 1b
    (1c) more than one element
    of $\componentsx{G\setminus e}$.
    %
    Case (2):
    $D$ and $L$ have non-empty intersection of edge sets, and $D$ is
    % originally 2
    (2a)
    a proper subgraph or
    % originally 3
    (2b)
    not a subgraph
    of $L$.
    %
    Note that this list is exhaustive. If $D$ and $L$ are edge disjoint, $D$ cannot contain subgraphs of elements of $\componentsx{G\setminus e}$. If $D$ and $L$ have non-empty intersection of edge sets, $D$ cannot be exactly $L$.
    See Figure~\ref{fig:seq_proof} for examples of the cases.

@@

    % Since each level of \branchGePG\ will contain some $L$ and $f\in L$ with a $D\in \componentsx{G\setminus f}$ that is either of Case (1a), (1c), or (2b) all nodes in the path from $G$ to $e$ can be found, which completes the proof.
    Since each node along the path from $e$ to $G$ is found by the above procedure, the proof is complete.
\end{proof}

>>>>

In this section and in Section~\ref{sec:recomb}, any reference to a graph $G$ without further specification is assumed to be isostatic (i.e.\ wellconstrained or $(k,l)$-tight). Furthermore, we only consider unions and intersections of graphs that are induced subgraphs of a single parent graph $G$. In this case unions and intersections are well defined. For example, the union (resp.\ intersection) of $F_1 = (V_1, E_1)$ and $F_2 = (V_2, E_2)$ is the subgraph of $G$ induced by $V_1\cup V_2$ (resp.\ $V_1\cap V_2$).

@@

    The proof of optimality of a canonical DR-plan is by induction on its height. The base case trivially holds for canonical DR-plans of height 0, i.e.\ for single edges. The induction hypothesis is that canonical DR-plans of height $t$ are optimal for the root node.
    For the induction step consider a canonical DR-plan $\candrpx{C}$ rooted at node $C$ with height $t+1$.
    Notice that $\candrpx{C}$ contains a canonical DR-plan $\candrpx{C_i}$ for the graphs $C_i$ corresponding to each of $C$'s descendant nodes.
    Thus, from the induction hypothesis, we know that the $\candrpx{C_i}$ is optimal for $C_i$.

@@

        % \newcommand{\induceonc}[1]{Idc\left(C,#1\right)}
        % \renewcommand{\induceonc}[1]{#1}
        % \newcommand{\iunion}[1]{\induceonc{I\cup\bigcup_{k\in [N]\setminus\{#1\}}{R_k}}}

@@

\begin{observation}
[\Pseudosequential\ is optimal]
    Any \pseudosequential\ DR-plan of an independent graph is optimal.
\end{observation}

@@

\begin{definition}
[\Branch]
    Given a \pseudosequential\ DR-plan $P_G$ for an isostatic graph $G$, and an edge $e \in G$, the \branchGePG\ is the subtree of the DR-plan consisting of the path from the root containing $G$ to the leaf containing $e$, together with the children of all the nodes on this path, which are the leaves of \branchGePG. See Figure~\ref{fig:seq_proof} for examples.
\end{definition}

@@

    Case (1):
    $D$ and $L$ are edge disjoint, and $D$ contains
    (1a) no elements,
    (1b) exactly one element, or
    % originally 1a and 1b
    (1c) more than one element
    of $\componentsx{G\setminus e}$.
    %
    Case (2):
    $D$ and $L$ have non-empty intersection of edge sets, and $D$ is
    % originally 2
    (2a)
    a proper subgraph or
    % originally 3
    (2b)
    not a subgraph
    of $L$.
    %
    Note that this list is exhaustive. If $D$ and $L$ are edge disjoint, $D$ cannot contain subgraphs of elements of $\componentsx{G\setminus e}$. If $D$ and $L$ have non-empty intersection of edge sets, $D$ cannot be exactly $L$.

@@

    % Since each level of \branchGePG\ will contain some $L$ and $f\in L$ with a $D\in \componentsx{G\setminus f}$ that is either of Case (1a), (1c), or (2b) all nodes in the path from $G$ to $e$ can be found, which completes the proof.
    Since each node along the path from $G$ to $e$ is found by the above procedure, the proof is complete.
    See Figure~\ref{fig:seq_proof} for examples of the cases.
\end{proof}
